---
title: "Assignment: Vector Operations and Data Types in R"
output:
  html_document:
    df_print: paged
---
In this exercise, we'll delve into vector creation, manipulation, and data type conversion in R, essential skills for data analysis.

**1.** Create a vector named `Jahre_var1` using the `c()` function with even numbers from 1983 to 2012. Then, do the same using the `seq()` function, but name this vector `Jahre_var2`.
```{r}
Jahre_var1 <- c(1983:2012)
Jahre_var1 <- Jahre_var1[Jahre_var1 %% 2 == 0]
print(Jahre_var1)

Jahre_var2 <- seq(1984, 2012, by = 2)
print(Jahre_var2)
```


**2.** Determine the data type of each vector. Convert them if necessary to match the appropriate data type for their contents. <br/>
```{r}
is.integer(Jahre_var1)

is.integer(Jahre_var2)
Jahre_var2 <- as.integer(Jahre_var2)
is.integer(Jahre_var2)
```


**3.** Now <br/>
   **a)** Convert the `Jahre_var1` vector to a character type. <br/>
```{r}
Jahre_var1 <- as.character(Jahre_var1)
str(Jahre_var1)
```

   **b)** After conversion, create two new vectors: `Massenzunahme` with values 4.52, 2, 12.04, 0, 8.432 and `AnzahlWochen` with values from 0 to 4. <br/>
```{r}
Massenzunahme <- c(4.52, 2, 12.04, 0, 8.432)
AnzahlWochen  <- seq(0, 4, 1)
```

   **c)** Divide `Massenzunahme` by `AnzahlWochen` and observe the results.
```{r}
Massenzunahme/AnzahlWochen
```



**4**. Then <br/>
**a)** Calculate the Shannon Index for a community of 4 species (A, B, C, D), where species A has 30 individuals, species B has 25 individuals, species C has 15 individuals, and species D has 10 individuals. The Shannon Index is calculated as follows:

$$
H = -\sum_{i=1}^{S} p_i \ln(p_i)
$$

with

$$
p_i = \frac{n_i}{N}
$$

where $n_i$ is the frequency of each species and $N$ is the total number of individuals across all species. Compare this with a community of 4 species, each having 12 individuals.

```{r}
N1 <- c(30, 25, 15, 10)
N2 <- rep(12, 4)
H1=-sum(N1/sum(N1)*log(N1/sum(N1)))
H2=-sum(N2/sum(N2)*log(N2/sum(N2)))
print(H1)
print(H2)
```
  
**b)** compare the result with a community of 4 species, each having 18 individuals.
```{r}
N3 <- rep(22, 4)
H3=-sum(N3/sum(N3)*log(N3/sum(N3)))
print(H3)
```


Please save your file as "FirstName_LastName_Task_Day2_Unit03.R".
