---
title: "Assignment: Objects and indexing in R"
output:
  html_document:
    df_print: paged
---

**1.** <br/>
   **a)** Create a vector named `vec1` with even numbers from 30 to 480, in steps of 3.<br/>
```{r}
vec1 <- seq(30, 480, by = 3)
print(vec1)
```

   **b)** How long is this vector? <br/>
```{r}
length_vec1 <- length(vec1)
print(length_vec1)
```
   
   **c)** Access the last element in the vector. <br/>
```{r}
last_element <- vec1[length(vec1)]
print(last_element)
```
   
   **d)** Extend the vector `vec1` by values from 480 to 494.<br/>
```{r, warning=FALSE}
vec1 <- c(vec1, 481:494)
print(vec1)
```
   
   **e)** Calculate the sum of `vec1`.
```{r}
sum_vec1 <- sum(vec1)
print(sum_vec1)
```
   

**2.** <br/>
   **a)** Create a matrix (named `mat1`) from `vec1` with 2 columns.<br/>
```{r}
mat1 <- matrix(vec1, ncol = 2)
print(mat1)
```
   
   **b)** Calculate the sum of `mat1`.<br/>
```{r}
sum_mat1 <- sum(mat1)
print(sum_mat1)
```
   
   **c)** Now create a matrix (named `mat2`) with 4 columns.<br
```{r}
mat2 <- matrix(vec1, ncol = 4)
print(mat2)
```

   **d)** Calculate the sum of `mat2`.<br/>
```{r}
sum_mat2 <- sum(mat2)
print(sum_mat2)
```
   
   **e)** What happened?<br/>
   Different sums because vector doesen't fit perfectly inside the matrix.
   **f)** Calculate the length of `vec1` divided by 5.<br/>
```{r}
length_div5 <- length(vec1) / 5
print(length_div5)
```
   
   **g)** Access the value at the 33rd row, 4th column of `mat2`.
```{r}
value_33_4 <- mat2[33, 4]
print(value_33_4)
```
   

**3.** <br/>
   **a)** Create a vector (`vec2`) with the first 10 letters of the alphabet (capitalized), each occurring 4 times. The class of this vector should be a factor. The factor levels should be in reverse order to the sequence in the alphabet (i.e., `A` should be listed as the last factor level when, for example, viewing the structure of the vector).<br/>
```{r}
vec2 <- factor(rep(LETTERS[1:10], each = 4), levels = rev(LETTERS[1:10]))
print(vec2)
```

   **b)** Reverse the levels of `vec2`.
```{r}
vec2 <- factor(vec2, levels = rev(levels(vec2)))
print(vec2)
```
   

**4.** Create a list named “list1” from `vec1`, `mat1`, `mat2`, and `vec2`. Assign appropriate names to the elements of the list. Access the 50th row, 15th column, of the 3rd element of this list.
```{r}
list1 <- list(vec1 = vec1, mat1 = mat1, mat2 = mat2, vec2 = vec2)
value <- list1$mat2[32, 3]
print(value)
```

**5.** <br/>
    **a)** Create a matrix that has as many columns and rows as `vec2` and name it `Dist`. It should be filled row-wise with values starting at 20.5, in steps of 1. <br/>
```{r}
num_elements <- length(vec2)
Dist <- matrix(seq(20.5, by = 1, length.out = num_elements), nrow = length(unique(vec2)), byrow = TRUE)
print(Dist)
```

   **b)** In the lower half of the matrix, for odd columns, divide the individual values by 2, and for even columns, subtract 100. Name the result Dist2.
```{r}
Dist2 <- Dist
rows <- nrow(Dist2)
cols <- ncol(Dist2)

lower_half_rows <- (rows/2 + 1):rows

# For odd columns in the lower half, divide values by 2
Dist2[lower_half_rows, seq(1, cols, 2)] <- Dist2[lower_half_rows, seq(1, cols, 2)] / 2

# For even columns in the lower half, subtract 100
Dist2[lower_half_rows, seq(2, cols, 2)] <- Dist2[lower_half_rows, seq(2, cols, 2)] - 100

print(Dist2)
```

    
    